### 2012-12-13 doc/description.tex
added definition of the set Label

There is a description of each component following. The description defines set of models of static components and dynamic components are defined as functions.
%TODO: prerequisities - lables (if they are unique it is not necessary to check the name)
%%%%%%%%%%%%%%%%%%%

\section{Application Component}
The application component represent an application created using object oriented language. It means the application is a set of instances which cooperates together. Each instance is defined according to a class - the class defines the structure, relationships of the instance. We use notation $instance \lhd class$ to describe the fact instance is defined according a class.

The application model consists of model of classes - structural model and of instances - data model. The whole application is described as:

$$
Application = (Class*, Instance*)
$$
%TODO: are instances necessary on this level?

The application is considered to be consistent if all instances are created according a class existing in the application. 
$$
\forall i \in instances(Application), \exists c \in classes(Application): i \lhd c 
$$
%TODO define consistency

@@

%TODO exist \rho to execute mapping and \rho' (?) just returning a name of mapped object

>>>>

There is a description of each component following. The description defines set of models of static components and dynamic components are defined as functions. There are several common parts of the model we can define in advance. The model uses a set $Labels$ which contains all possible identifiers for the model. Each model component which has a label ($label \in Labels$) is unambiguously identified in the model.

\section{Application Component}
The application component represent an application created using object oriented language. It means the application is a set of instances which cooperates together. Each instance is defined according to a class - the class defines the structure and relationships of the instance. 
The application component model consists of  classes defining the structure of application:

$$
Application = (Class*)
$$

@@
